The Essence of Summarization\\ in Pushdown Flow Analyses\\ \textbf{Supplemental Material}

### 2014-03-24 content.tex
Added more to the argument of correctness for delimited control, plus a discussion of similarity with CFA2's approach for call/cc.

%%
This paper gives a common, simple methodology to derive CFA2, PDCFA and its garbage-collecting extension in a manner similar to AAM.
%
Our presentation is meant to be a tutorial to this related literature, with the additional promise of a novel analysis.
%
We don't presume a language of formal semantics such that our technique applies to all formalisms in such a language.
%
An overly formal approach is unlikely to capture all ``real language's'' formalizations.
%
The additional abstraction also detracts from the operational intuitions and simplicity of the methodology.

@@

%%
This paper extends the work providing \rackett{call/cc} by giving an operational view of what summarization is, in essence.
%
In other words, we give a concrete semantics to the algorithmic techniques that the analyses in the literature use in the abstract, and maintain the original meaning of the language.
%
We also give intuitive analogies to well-established ideas and techniques so that the working semanticist can write a pushdown analysis for their language.
%
In order to demonstrate the applicability of this viewpoint, we show a new analysis for a language with composable control.
%
All of the semantics modeled in this paper are implemented in full detail in PLT Redex~\citep{ianjohnson:Felleisen:2009:SEP:1795772} and available online.\footnote{\url{http://github.com/ianj/concrete-summaries}}

@@

The table-based semantics makes prompts a point of indirection, just like function calls.
%
Memoization also gets a new context to consider, calling a continuation, because composable continuations act like functions.
%
The new semantic spaces are then

\begin{align*}
  \mctx \in \Context &::= (\mexpr,\menv,\mstore) \alt (\vcomp{\mkont},\mval,\mstore) \\
  \mkont \in \Kont &= \kmt \alt \krt{\mctx} \alt \kcons{\mkframe}{\mkont} \\
  \mmkont \in \MKont &::= \kmt \alt \kprompt{\mctx} \\
  \mathit{KRange} &= \wp(\Kont \times \MKont) \cup \wp(\Kont) \\
  \mktab \in \KTab &= \Context \to \mathit{KRange} \\
  \mmemo \in \Memo &= \Context \to \wp(\Value \times \Store)
\end{align*}

@@

\begin{figure*}
  \centering
  $\mstate \stepto \mstate' \text{ where } \maddr = \alloc(\mstate)$ \\
  \begin{tabular}{r|l}
    \hline
% Reset
    $\tpl{\sreset{\mexpr}, \menv, \mstore, \mkont, \mmkont, \mktab, \mmemo}$
    &
    $\tpl{\mpoint, \mstore, \kmt, \kprompt{\mctx}, \joinone{\mktab}{\mctx}{(\mkont,\mmkont)}, \mmemo}$
    \\
    where & $\mpoint = (\mexpr, \menv)$, $\mctx = (\mpoint, \mstore)$.
    \\
% Pop prompt
    $\tpl{\mval, \mstore, \kmt, \kprompt{\mctx}, \mktab, \mmemo}$
    &
    $\tpl{\mval, \mstore, {\mkont}, {\mmkont}, \mktab, \joinone{\mmemo}{\mctx}{(\mval,\mstore)}}$
    if $(\mkont,\mmkont) \in \mktab(\mctx)$
    \\
% Shift
    $\tpl{\sshift{\mvar}{\mexpr}, \menv, \mstore, \mkont, \mmkont, \mktab, \mmemo}$
    &
    $\tpl{\mexpr, \extm{\menv}{\mvar}{\maddr}, \joinone{\mstore}{\maddr}{\vcomp{\mkont}},\kmt,\mmkont,\mktab,\mmemo}$
    \\
% continuation call
    $\tpl{\mval,\mstore,\kcons{\kfn{\vcomp{\mkont'}}}{\mkont}, \mmkont, \mktab, \mmemo}$
    &
    $\tpl{\mval, \mstore, \mkont', \kprompt{\mctx}, \mktab',\mmemo}$
    \\ & \quad if $\mctx \notin \dom(\mmemo)$
    \\
    & or \\
    & $\tpl{\mval', \mstore', \mkont, \mmkont, \mktab',\mmemo}$
    \\ & \quad if $(\mval',\mstore') \in \mmemo(\mctx)$
    \\
    where & $\mctx = (\vcomp{\mkont'}, \mval, \mstore)$ \\
          & $\mktab' = \joinone{\mktab}{\mctx}{(\mkont,\mmkont)}$
    \\
% Memoized continuation call
% continuation call
    $\tpl{\mval,\mstore,\kcons{\kfn{\vcomp{\mkont'}}}{\mkont}, \mmkont, \mktab, \mmemo}$
    &
    $\tpl{\mval', \mstore', \mkont, \mmkont, \mktab,\mmemo}$ if $(\mval',\mstore') \in \mmemo(\vcomp{\mkont'},\mval,\mstore)$
  \end{tabular}  
  \caption{Faulty table-based semantics for shift/reset}
  \label{fig:shift-reset-table0}
\end{figure*}

@@

\begin{figure*}
  \centering
% Shift
  $\mstate \stepto \mstate' \text{ where } \maddr = \alloc(\mstate)$ \\
  \begin{tabular}{r|l}
    \hline
    $\tpl{\sshift{\mvar}{\mexpr}, \menv, \mstore, \mkont, \mmkont, \mmktab, \mktab, \mmemo}$
    &
    $\tpl{\mexpr, \extm{\menv}{\mvar}{\maddr}, \mstore',\kmt,\mmkont, \mmktab', \mktab,\mmemo}$
    \\
    where & $\mstore' = \joinone{\mstore}{\maddr}{\vcomp{\mkont'}}$ \\
    & $(\mkont',\mmktab') = \approximate(\mkont, \mmktab, \maddr)$
\\
% Return
   $\tpl{\mval, \mstore, \krt{\mctx}, \mmkont, \mmktab, \mktab, \mmemo}$
   &
   $\tpl{\mval, \mstore, \mkont, \mmkont, \mmktab, \mktab, \mmemo'}$
   if $\mkont \in \returns(\mmktab, \mktab, \mctx)$
   \\
   where & $\mmemo' = \mmemo \sqcup \memoize(\mmktab, \mktab, \mctx, (\mval, \mstore, \mmktab))$
  \end{tabular}
  \caption{Fixed table-based semantics for shift/reset}
  \label{fig:shift-reset-table1}
\end{figure*}

@@

\newcommand{\replacectx}{\hat\mkont} %\mathit{replace}\mstore
\newcommand{\addstore}{\hat\mmktab} % \mathit{add}\mstore
\begin{center}
  $\approximate(\mkont, \mmktab, \maddr) = (\replacectx(\mkont), \addstore(\mkont)) \text{ where}$\\
  \begin{minipage}{0.45\linewidth}
    \begin{align*}
      \replacectx(\kmt) &= \kmt \\
      \replacectx(\krt{(\mexpr,\menv,\ldots)}) &= \krt{(\mexpr,\menv,\maddr)} \\
      \replacectx(\kcons{\mkframe}{\mkont}) &=
      \kcons{\mkframe}{\replacectx(\mkont)}
    \end{align*}
  \end{minipage}
  \begin{minipage}{0.50\linewidth}
    \begin{align*}
      \addstore(\kmt) &= \mmktab \\
      \addstore(\krt{(\mexpr,\menv,\mstore,\mmktab')}) &= \joinone{\mmktab}{\maddr}{\mstore}\sqcup \mmktab' \\
      \addstore(\krt{(\mexpr,\menv,\maddr')}) &= \joinm{\mmktab}{\maddr}{\mmktab(\maddr')} \\
      \addstore(\kcons{\mkframe}{\mkont}) &= \addstore(\mkont)
    \end{align*}
  \end{minipage}
\end{center}
%
If the context in an $\rt$ continuation is approximate, we must return to all the continuations known for all the contexts it approximates:
\begin{align*}
  &\returns(\mmktab, \mktab, (\mexpr,\menv, \mstore, \mmktab')) = \mktab(\mexpr,\menv, \mstore, \mmktab') \\
  &\returns(\mmktab, \mktab, (\mexpr,\menv, \maddr)) =
    \bigcup\setbuild{\mktab(\mexpr,\menv,\mstore,\mmktab')}{\mstore \in \mmktab(\maddr), \mmktab' \sqsubseteq \mmktab}
\end{align*}

At returns, the memo table must add the result to all represented contexts:
\newcommand{\res}{m}
\begin{align*}
  &\memoize(\mmktab, \mktab, (\mexpr,\menv, \mstore', \mmktab'), \res) =
  [(\mexpr,\menv, \mstore',\mmktab') \mapsto \set{{\res}}] \\
  &\memoize(\mmktab, \mktab, (\mexpr,\menv, \maddr), \res) = [\mctx \mapsto \set{\res} : \mctx \in \dom(\mktab) \cap C] \\
  &\text{where } C = \setbuild{(\mexpr,\menv, \mstore', \mmktab')}{\mstore' \in \mmktab(\maddr), \mmktab' \sqsubseteq \mmktab}
\end{align*}

@@

@@

>>>>

%%
This paper gives a common, simple methodology to derive CFA2, PDCFA and its garbage-collecting extension in a manner similar to AAM.
%
Our presentation is meant to be a tutorial to this related literature, with the additional promise of a novel analysis.
%
We don't presume a language of formal semantics such that our technique applies to all formalisms in such a language.
%
An overly formal approach is unlikely to capture all ``real language's'' formalizations.
%
The additional abstraction also detracts from the operational intuitions and simplicity of the methodology.
%
We still present the definitions and proofs in a manner that should be well-positioned for mechanization.
%
This paper has been partially mechanized in the Coq proof assistant, with proofs in the supplemental materials\footnote{\url{http://github.com/ianj/concrete-summaries} in \texttt{model.v}}.

@@

%%
This paper extends the work providing \rackett{call/cc} by giving an operational view of what summarization is, in essence.
%
In other words, we give a concrete semantics to the algorithmic techniques that the analyses in the literature use in the abstract, and maintain the original meaning of the language.
%
We also give intuitive analogies to well-established ideas and techniques so that the working semanticist can write a pushdown analysis for their language.
%
In order to demonstrate the applicability of this viewpoint, we show a new analysis for a language with composable control.
%
All of the semantics modeled in this paper are implemented in full detail in PLT Redex~\citep{ianjohnson:Felleisen:2009:SEP:1795772} and available in the supplemental materials.

@@

The table-based semantics makes prompts a point of indirection, just like function calls.
%
Memoization also gets a new context to consider, calling a continuation, because composable continuations act like functions.
%
We separate contexts stored in meta-continuations from those in continuations to avoid losing precision from abstracting continuations' contexts.
%
The table for continuations is treated the same way as in the previous semantics for standard function call and return.
%
The new semantic spaces are then

\begin{align*}
  \mctx \in \Context &::= (\mexpr,\menv,\mstore) \alt (\vcomp{\mkont},\mval,\mstore) \\
  \mkont \in \Kont &= \kmt \alt \krt{\mctx} \alt \kcons{\mkframe}{\mkont} \\
  \mmkont \in \MKont &::= \kmt \alt \kprompt{\mctx} \\
  \mathit{KRange} &= \wp(\Kont \times \MKont) \cup \wp(\Kont) \\
  (\mktab_\mkont,\mktab_\mmkont) \in \KTab &= (\Context \to \wp(\Kont)) \\
                                        &\times (\Context \to \wp(\Kont \times \MKont)) \\
  \mmemo \in \Memo &= \Context \to \wp(\Value \times \Store)
\end{align*}

@@

\begin{figure*}
  \centering
  $\mstate \stepto \mstate' \text{ where } \maddr = \alloc(\mstate)$ \\
  \begin{tabular}{r|l}
    \hline
% Reset
    $\tpl{\sreset{\mexpr}, \menv, \mstore, \mkont, \mmkont, (\mktab_\mkont,\mktab_\mmkont), \mmemo}$
    &
    $\tpl{\mpoint, \mstore, \kmt, \kprompt{\mctx}, (\mktab_\mkont,\joinone{\mktab_\mmkont}{\mctx}{(\mkont,\mmkont)}), \mmemo}$
    \\
    where & $\mpoint = (\mexpr, \menv)$, $\mctx = (\mpoint, \mstore)$.
    \\
% Pop prompt
    $\tpl{\mval, \mstore, \kmt, \kprompt{\mctx}, \mktab\equiv(\mktab_\mkont,\mktab_\mmkont), \mmemo}$
    &
    $\tpl{\mval, \mstore, {\mkont}, {\mmkont}, \mktab, \joinone{\mmemo}{\mctx}{(\mval,\mstore)}}$
    if $(\mkont,\mmkont) \in \mktab_\mkont(\mctx)$
    \\
% Shift
    $\tpl{\sshift{\mvar}{\mexpr}, \menv, \mstore, \mkont, \mmkont, \mktab, \mmemo}$
    &
    $\tpl{\mexpr, \extm{\menv}{\mvar}{\maddr}, \joinone{\mstore}{\maddr}{\vcomp{\mkont}},\kmt,\mmkont,\mktab,\mmemo}$
    \\
% continuation call
    $\tpl{\mval,\mstore,\kcons{\kfn{\vcomp{\mkont'}}}{\mkont}, \mmkont, (\mktab_\mkont,\mktab_\mmkont), \mmemo}$
    &
    $\tpl{\mval, \mstore, \mkont', \kprompt{\mctx}, (\mktab_\mkont,\mktab_\mmkont'),\mmemo}$
    \\ & \quad if $\mctx \notin \dom(\mmemo)$
    \\
    & or \\
    & $\tpl{\mval', \mstore', \mkont, \mmkont, (\mktab_\mkont,\mktab_\mmkont'),\mmemo}$
    \\ & \quad if $(\mval',\mstore') \in \mmemo(\mctx)$
    \\
    where & $\mctx = (\vcomp{\mkont'}, \mval, \mstore)$ \\
          & $\mktab_\mmkont' = \joinone{\mktab_\mmkont}{\mctx}{(\mkont,\mmkont)}$
    \\
% Memoized continuation call
% continuation call
    $\tpl{\mval,\mstore,\kcons{\kfn{\vcomp{\mkont'}}}{\mkont}, \mmkont, \mktab, \mmemo}$
    &
    $\tpl{\mval', \mstore', \mkont, \mmkont, \mktab,\mmemo}$ if $(\mval',\mstore') \in \mmemo(\vcomp{\mkont'},\mval,\mstore)$
  \end{tabular}  
  \caption{Faulty table-based semantics for shift/reset}
  \label{fig:shift-reset-table0}
\end{figure*}

@@

\begin{figure*}
  \centering
% Shift
  $\mstate \stepto \mstate' \text{ where } \maddr = \alloc(\mstate)$ \\
  \begin{tabular}{r|l}
    \hline
    $\tpl{\sshift{\mvar}{\mexpr}, \menv, \mstore, \mkont, \mmkont, \mmktab, \mktab, \mmemo}$
    &
    $\tpl{\mexpr, \extm{\menv}{\mvar}{\maddr}, \mstore',\kmt,\mmkont, \mmktab', \mktab,\mmemo}$
    \\
    where & $\mstore' = \joinone{\mstore}{\maddr}{\vcomp{\mkont'}}$ \\
    & $(\mkont',\mmktab') = \approximate(\mkont, \mmktab, \maddr)$
\\
% Return
   $\tpl{\mval, \mstore, \krt{\mctx}, \mmkont, \mmktab, \mktab\equiv(\mktab_\mkont,\mktab_\mmkont), \mmemo}$
   &
   $\tpl{\mval, \mstore, \mkont, \mmkont, \mmktab, \mktab, \mmemo'}$
   if $\mkont \in \returns(\mmktab, \mktab_\mkont, \mctx)$
   \\
   where & $\mmemo' = \mmemo \sqcup \memoize(\mmktab, \mktab_\mkont, \mctx, (\mval, \mstore, \mmktab))$
  \end{tabular}
  \caption{Fixed table-based semantics for shift/reset}
  \label{fig:shift-reset-table1}
\end{figure*}

@@

\newcommand{\replacectx}{\hat\mkont} %\mathit{replace}\mstore
\newcommand{\addstore}{\hat\mmktab} % \mathit{add}\mstore
\begin{center}
  $\approximate(\mkont, \mmktab, \maddr) = (\replacectx(\mkont), \addstore(\mkont)) \text{ where}$\\
  \begin{minipage}{0.45\linewidth}
    \begin{align*}
      \replacectx(\kmt) &= \kmt \\
      \replacectx(\krt{(\mexpr,\menv,\ldots)}) &= \krt{(\mexpr,\menv,\maddr)} \\
      \replacectx(\kcons{\mkframe}{\mkont}) &=
      \kcons{\mkframe}{\replacectx(\mkont)}
    \end{align*}
  \end{minipage}
  \begin{minipage}{0.50\linewidth}
    \begin{align*}
      \addstore(\kmt) &= \mmktab \\
      \addstore(\krt{(\mexpr,\menv,\mstore,\mmktab')}) &= \joinone{\mmktab}{\maddr}{\mstore}\sqcup \mmktab' \\
      \addstore(\krt{(\mexpr,\menv,\maddr')}) &= \joinm{\mmktab}{\maddr}{\mmktab(\maddr')} \\
      \addstore(\kcons{\mkframe}{\mkont}) &= \addstore(\mkont)
    \end{align*}
  \end{minipage}
\end{center}
%
If the context in an $\rt$ continuation is approximate, we must return to all the continuations known for all the contexts it approximates:
\begin{align*}
  &\returns(\mmktab, \mktab_\mkont, (\mexpr,\menv, \mstore, \mmktab')) = \mktab_\mkont(\mexpr,\menv, \mstore, \mmktab') \\
  &\returns(\mmktab, \mktab_\mkont, (\mexpr,\menv, \maddr)) =
    \bigcup\setbuild{\mktab_\mkont(\mexpr,\menv,\mstore,\mmktab')}{\mstore \in \mmktab(\maddr), \mmktab' \sqsubseteq \mmktab}
\end{align*}

At returns, the memo table must add the result to all represented contexts:
\newcommand{\res}{m}
\begin{align*}
  &\memoize(\mmktab, \mktab_\mkont, (\mexpr,\menv, \mstore', \mmktab'), \res) =
  [(\mexpr,\menv, \mstore',\mmktab') \mapsto \set{{\res}}] \\
  &\memoize(\mmktab, \mktab_\mkont, (\mexpr,\menv, \maddr), \res) = [\mctx \mapsto \set{\res} : \mctx \in \dom(\mktab_\mkont) \cap C] \\
  &\text{where } C = \setbuild{(\mexpr,\menv, \mstore', \mmktab')}{\mstore' \in \mmktab(\maddr), \mmktab' \sqsubseteq \mmktab}
\end{align*}

@@

This theorem amounts to just the first bullet of \autoref{thm:concrete-tabular}.
%
The definition of ${\mathcal F}$ is similar in that only $\mktab$ and $\mmemo$ are widened, but states in $R$ now also contain $\mmkont$s and $\mmktab$s.
%
The definition of $\reify$ must change to account for the different target state space, the new context form and the continuation closure:
\\

  $\reify(F, R, \mktab, \mmemo) =$
\begin{align*}
  &\quad \{ (\tpl{\mpoint,\mstore,\mkont_0,\mmkont_0},
              \tpl{\mpoint',\mstore',\mkont_1,\mmkont_1})\ :\ 
\\ &\qquad E\equiv(\tpl{\mpoint,\mstore,\mkont,\mmkont,\mmktab}, \tpl{\mpoint',\mstore',\mkont',\mmkont',\mmktab'}) \in R\text,
\\ &\qquad((\mkont_0,\mmkont_0),(\mkont_1,\mmkont_1)) \in \mathit{conts}_\mktab^\mmktab(E) \}
\end{align*}

The $\mathit{conts}$ function needs to inspect the reduction actually used to know if the meta-continuation is pushed, popped, or stays the same.
%
We'll classify the different reductions as such in the in the definition of $\mathit{conts}$ to not obfuscate the intended meaning.
%
We'll use $(\mkont,\kprompt{\mctx}) \overset{+}{\to} (\mkont',\kprompt{\mctx'})$ for a pushed continuation from a meta-continuation $\kprompt{\mctx}$ to $\kprompt{\mctx'}$, which happens in the \texttt{reset} and continuation invocation rules.
%
Similarly, the prompt-popping rule is marked as $(\kmt,\kprompt{\mctx}) \overset{-}{\to} (\mkont,\kprompt{\mctx'})$, since it replaces the $\kmt$ with some $\mkont$ and changes the prompt's context.
%
We don't need to inspect the second context since its unrolling will include the pushed/popped continuations.

\begin{center}
  \begin{tabular}{l}
    $\mathit{conts}_\mktab^\mmktab((\mkont,\mmkont) \overset{+}{\to} (\mkont',\mmkont')) =$ \\
    \quad$\setbuildb{((\mkont_0,\mmkont^*),(\mkont_1,\mkapp{\mkont_0}{\mmkont^*}))}
    {
      \begin{array}{l}
        \mkont_0 \in \unrollK{\mmktab}{\mktab_\mkont}{\mkont}, \\
        \mkont_1 \in \unrollK{\mmktab}{\mktab_\mkont}{\mkont'}, \\
        \mmkont^* \in \unrollC{\mktab_\mmkont}{\mmkont}
      \end{array}}$
    \\
%
    $\mathit{conts}_\mktab^\mmktab((\mkont,\mmkont) \to (\mkont',\mmkont)) =$ \\
    \quad$\setbuildb{((\append{\mkont}{\mkont''},\mmkont), (\append{\mkont'}{\mkont''}, \mmkont))}
    {\begin{array}{l}
        \mkont'' \in \tails{\mktab_\mkont}{\mkont}, \\
        \mmkont \in \unrollC{\mktab}{\mmkont}
      \end{array}}$
    \\
%
    $\mathit{conts}_\mktab^\mmktab((\kmt,\kprompt{\mctx}) \overset{-}{\to} (\mkont,\kprompt{\mctx'})) =$ \\
    \quad$\setbuildb{((\kmt,\mkapp{\mkont'}{\mmkont'}),(\mkont',\mmkont'))}{
    \begin{array}{l}
      (\mkont,\mmkont) \in \mktab_\mmkont(\mctx), \\
      \mkont' \in \unrollK{\mmktab}{\mktab_\mkont}{\mkont}, \\
      \mmkont' \in \unrollC{\mktab_\mmkont}{\mmkont}
    \end{array}}$
  \end{tabular}
\end{center}

\begin{align*}
  \unrollK{\mmktab}{\mktab_\mkont}{\mkont} &= \setbuild{\append{\mkont}{\mkont'}}{\mkont' \in \tailscont{\mktab_\mkont}{\mmktab}{\mkont}}
\\[2pt]
  \tailscont{\mktab_\mkont}{\mmktab}{\mkont}(\kmt) &= \set{\kmt} \\
  \tailscont{\mktab_\mkont}{\mmktab}{\mkont}(\kcons{\mkframe}{\mkont}) &= \tailscont{\mktab_\mkont}{\mmktab}{\mkont} \\
  \tailscont{\mktab_\mkont}{\mmktab}{\mkont}(\krt{\mctx}) &= \bigcup\limits_{\mkont \in \returns(\mmktab,\mktab_\mkont,\mctx)}{\unrollK{\mmktab}{\mktab_\mkont}{\mkont}}
\\[2pt]
  \unrollC{\mktab}{\kmt} &= \set{\kmt} \\
  \unrollC{(\mktab_\mkont,\mktab_\mmkont)}{\kprompt{\mctx}} &=
    \setbuild{\mkapp{\mkont'}{\mmkont'}}{(\mkont,\mmkont) \in \mktab_\mmkont(\mctx),
      \\&\phantom{= \{}\quad \mkont' \in \unrollK{\mmktab}{\mktab_\mkont}{\mkont},
      \\&\phantom{= \{}\quad \mmkont' \in \unrollC{\mktab}{\mmkont}}
\end{align*}

@@

\paragraph{Comparison to CFA2 and \texttt{call/cc}}
Although we make no formal comparison of the constructions in this paper that those of CFA2, we can point out similarities in the approaches.
%
We claim that what we showed in this section marks a strict generalization of the methods in \citet{dvanhorn:Vardoulakis2011Pushdown}.
%
CFA2 makes a specific choice of parameters for context-sensitivity and heap abstraction.
%
If we specialize this work to a monovariant allocation strategy and a global store widening, the utility of a continuation closure $\mmktab$ becomes moot, since the store is monotonically increasing.
%
In other words, any distinction between contexts that we might hope to achieve given a $\mmktab$ will fail since the $\mmktab' \sqsubseteq \mmktab$ proposition in the $\returns$ meta-function will always be true.
%
With this realization, we can look closer at what happens when invoking a continuation.
%
Once execution reaches the $\krt{\mctx}$ tail of an installed captured continuation, $\returns$ will ensure flow continues to absolutely every context that captured that continuation.
%
For the readers making the comparison themselves, lines 28 and 29 of CFA2's workset algorithm embody this flow explosion rule.
%
To paraphrase, whenever execution reaches the invocation of a captured continuation, every call of the function that captures the continuation is marked as returning with the value passed to the continuation (remember, non-compositional continuations act like returns and not calls).
%
Since we semantically distinguish captured continuations from non-captured, we don't need any judgement about the heap-allocation of certain bindings that CFA2 uses.
